One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2024-10-28 paper.tex
add bird data to data availability statement

@@

The \hawaii \akepa{} data are provided by U.S. Fish and Wildlife Service, Hakalau Forest Unit National Wildlife Refuge. We are grateful to the many U.S. Fish and Wildlife Service staff and volunteers who helped collect the data. We thank Steve Buckland for helpful comments on an early version.  Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.

>>>>

\section*{Data Availability}

Hawaii Akepa (Loxops coccineus) point-transect distance sampling data were provided by U.S. Fish and Wildlife Service, Hakalau Forest Unit of the Big Island National Wildlife Refuge Complex. The 2002 survey data are available from the U.S. Geological Survey: \url{https://doi.org/10.5066/P9Q9UXMZ} \citep{camp_datarelease_2002}.  The time data for 1987-2017 is also available  available from the U.S. Geological Survey: \url{https://doi.org/10.5066/P98IO297} \citep{camp_datarelease_all}

Code to reproduce the figures and results in this paper are available in a git repository and can be accessed at [git repo link].

@@

We are grateful to the many U.S. Fish and Wildlife Service staff and volunteers who helped collect the data through the Hawaiian Forest Bird survey. We thank Steve Buckland for helpful comments on an early draft.  Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.
